When does VPD drive or reduce ET?

### 2017-10-20 doc/glab_meeting_2017-10-20/vpd.tex
added vpd, calling it quits fo rthe night

\title[Your Short Title]{Bayesian Neural  Networks and Probalistic Programming}
\author{Adam Massmann and Laureline Josset}
\institute{Water Center NN Meetings}
\date{Week 5: Oct. 17th, 2017}

@@

>>>>

\title[Your Short Title]{When does VPD drive or reduce ET?}
\author{Adam with Pierre and Changjie}
\institute{G-Lab Meeting}
\date{October 20th, 2017}

@@

\begin{frame}{When does VPD drive or reduce ET?}
  \begin{itemize}
  \item \textbf{Hydrometeorologists} would say that an increase in VPD (increase in \textbf{atmospheric demand}) would drive an \textbf{increase in ET}.
  \item However, \textbf{plant physioligists} know that plants have evolved to use stomata to conserve and regulate water use. So \textbf{stomata closure} in response to increases in VPD may \textbf{decrease ET}.
  \end{itemize}
\end{frame}

\begin{frame}{The question is, which effect dominates with an increase in VPD: plant response (decrease in ET) or atmospheric demand (increase in ET)?}
  \begin{itemize}
  \item We hypothesize it will be a function of plant type and the environment:
    \begin{itemize}
    \item Plants that are evolved to conserve water will tend to reduce ET with increases in VPD.
    \item However the environment can overwhelm plant response: at very high VPD the atmospheric demand will dominate and plants will not be able to consernve water, no matter how much they have evolved to do so.
    \end{itemize}
  \end{itemize}
\end{frame}
